---
title: "Journal (reproducible report)"
author: "Khaled Al-Zaben"
date: "2020-11-23"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```


# Into the tidyverse

Into the tidyverse

## Challenge 1

Analyze the sales by location (state) with a bar plot. Since state and city are multiple features (variables), they should be split. Which state has the highes revenue? Replace your bike_orderlines_wrangled_tbl object with the newly wrangled object (with the columns state and city).

## Challenge 2

Analyze the sales by location and year (facet_wrap). Because there are 12 states with bike stores, you should get 12 plots.

## Challenge Code
```{r, code=readLines("Intro_to_the_tidyverse.R")}
```


# Data Acquisition

Data Acquisition

## Challenge 1

Get some data via an API. There are millions of providers, that offer API access for free and have good documentation about how to query their service. You just have to google them. You can use whatever service you want. For example, you can get data about your listening history (spotify), get data about flights (skyscanner) or just check the weather forecast.

## Challenge Code
```{r, code=readLines("Data Acquisition_API.R")}
```

## Challenge 2

Scrape one of the competitor websites of canyon (either https://www.rosebikes.de/ or https://www.radon-bikes.de) and create a small database. The database should contain the model names and prices for at least one category. Use the selectorgadget to get a good understanding of the website structure.

## Challenge Code
```{r, code=readLines("Data Acquisition_webscraping.R")}
```

# Data Wrangling

Data Wrangling

## Challenge 

Answer the following questions with that data:

1- Patent Dominance: What US company / corporation has the most patents? List the 10 US       companies with the most assigned/granted patents.   
2- Recent patent acitivity: What US company had the most patents granted in 2019? List the top 10 companies with the most new granted patents for 2019.    
3- Innovation in Tech: What is the most innovative tech sector? For the top 10 companies (worldwide) with the most patents, what are the top 5 USPTO tech main classes?    

## Challenge Code
 
library(tidyverse)
library(vroom)
library(magrittr)
library(lubridate)
library(data.table)

patent <-  "C:/Users/Khale/Desktop/Business Module/DS_101/02_data_wrangling/patent.tsv"
patent_tbl <- fread(patent)
setnames(patent_tbl, "id", "patent_id")
patent_tbl_view <- patent_tbl[1:2]

assignee  <-   "C:/Users/Khale/Desktop/Business Module/DS_101/02_data_wrangling/assignee.tsv"
assignee_tbl <- fread(assignee)
setnames(assignee_tbl, "id", "assignee_id")

patent_assignee <- "C:/Users/Khale/Desktop/Business Module/DS_101/02_data_wrangling/patent_assignee.tsv"
patent_assignee_tbl<- fread(patent_assignee)

uspc <- "C:/Users/Khale/Desktop/Business Module/DS_101/02_data_wrangling/uspc.tsv"
uspc_tbl<- fread(uspc)
setnames(uspc_tbl, "uuid", "assignee_id")

combined_data_assignee <- merge(assignee_tbl, patent_assignee_tbl, by='assignee_id')
na.omit(combined_data_assignee, cols="organization")


combined_data_assignee [, .N, by = organization][order(-N)] %>% head(1)%>%na.omit()


combined_data_assignee [, .N, by = organization][order(-N)]%>%na.omit() %>% head(11)

combined_data_patent <- merge(combined_data_assignee,patent_tbl , by='patent_id') 
reshaped_patent_tbl <- combined_data_patent[,.(patent_id, country, date, organization,kind)]

reshaped_patent_tbl [lubridate::year(date) == 2019, .N, by = organization][order(-N)]%>%na.omit() %>% head(1)

reshaped_patent_tbl [lubridate::year(date) == 2019 & kind=="B1", .N, by = organization][order(-N)]%>%na.omit() %>% head(10)

combined_data_uspc <- merge(combined_data_assignee,uspc_tbl , by='patent_id') 
reshaped_uspc_tbl <- combined_data_uspc[,.(patent_id, type, organization,mainclass_id,subclass_id)]

patent_tbl[, .N, by = type][order(-N)] %>% head(1)

reshaped_uspc_tbl[organization=="International Business Machines Corporation", .N, by = mainclass_id][order(-N)]%>% head(5)

## Challenge 1

1st output

                                        organization      N                              
      1: International Business Machines Corporation 139091
      
2nd Output

                                       organization      N    
     1: International Business Machines Corporation 139091  
     2:               Samsung Electronics Co., Ltd.  93561  
     3:                      Canon Kabushiki Kaisha  75909  
     4:                                              73070  
     5:                            Sony Corporation  54342  
     6:                    Kabushiki Kaisha Toshiba  49442  
     7:                    General Electric Company  47121  
     8:                               Hitachi, Ltd.  45374  
     9:                           Intel Corporation  42156  
    10:                             Fujitsu Limited  37196

## Challenge 2

1st output

                                        organization    N  
      1: International Business Machines Corporation 9265
      
2nd output

                                              organization    N
         1:                      Amazon Technologies, Inc. 1766  
         2:                     EMC IP Holding Company LLC  719  
         3:                                    Google Inc.  550  
         4:    International Business Machines Corporation  515  
         5:                      Capital One Services, LLC  386  
         6:                                     Apple Inc.  299  
         7:                                                 276  
         8: STATE FARM MUTUAL AUTOMOBILE INSURANCE COMPANY  242  
         9:                                 Facebook, Inc.  239  
        10:            Pioneer Hi-Bred International, Inc.  233      

## Challenge 3

  1st output 
  
                      type       N    
                1: utility 6735315
      
2nd output 

           mainclass_id     N  
        1:          257 21754  
        2:          709 16834  
        3:          438 16596  
        4:          707 16147  
        5:          711 12829


# Data Visualization

Data Visualization

## Challenge 1

Goal: Map the time course of the cumulative Covid-19 cases!
Adding the cases for Europe is optional. You can choose your own color theme, but don’t use the default one. Don’t forget to scale the axis properly. The labels can be added with geom_label() or with geom_label_repel() (from the package ggrepel).

## Challenge Code
```{r, code=readLines("data_visualization_E1.R")}
```

## Challenge 2

Goal: Visualize the distribution of the mortality rate (deaths / population) with geom_map(). 

## Challenge Code
```{r, code=readLines("data_visualization_E2.R")}
```


